Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-11-20 referee_2.tex
Adding a note in the response
Removed previous bold text. Responded to all referee comments and have made adjustments to the paper. Still have a few questions and things to finish up leftover regarding the last comment.

We thank the referee for their response to our recent revision. Their review is directly quoted below in the gray boxes with our responses below.  Any changes to the manuscript, as well as changes made previously, have been \textbf{bold-faced}.

@@

    --need to add to Caveats
    --adjust some wording about Pop III star formation regions?

    \jhw{I've add some wording in Sections 2.2.1 and 3.3 about fragmentation and our study being a lower limit on the multiplicity but nothing to the caveats section. I think with these statements, we can argue in the response that changes throughout the text are not needed.}

@@

    O'Shea and Norman 2008 do not provide an analytic fit for the H$_2$ radial profile. The profile used in our calculations were taken from their figure 13 panel d. This detail has been added in the description of the H$_2$ radial profiles.

    \jhw{You should give the exact fitting formula in the text.}

@@

\begin{referee}
    H -- - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal. They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions. Please include their limits in your Figure 10, as done with the Naoz+13 results, and a short comparison to Hirano+18 (their Science paper). Please include these references also in the introduction. Also the sentence "Often in the literature, streaming velocities are only studied for a few haloes" seems outdated.
\end{referee}

>>>>

We thank the referee for their response to our recent revision. Their review is directly quoted below in the gray boxes with our responses below.  Any changes to the manuscript, have been \textbf{bold-faced}.

@@

    --Added to the caveats

    \jhw{I've add some wording in Sections 2.2.1 and 3.3 about fragmentation and our study being a lower limit on the multiplicity but nothing to the caveats section. I think with these statements, we can argue in the response that changes throughout the text are not needed. Make the changes to the caveats section, and I'll write the rebuttal here.}

@@

    Our fitting formula has been added to the text where their H2 profiles are discussed.

@@

\begin{referee}
    H -- - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal. They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions. Please include their limits in your Figure 10, as done with the Naoz+13 results, and a short comparison to Hirano+18 (their Science paper). Please include these references also in the introduction. Also the sentence "Often in the literature, streaming velocities are only studied for a few haloes" seems outdated.
\end{referee}
	The limits from Schauer+19 have been added to Figure 10, and the previous description regarding the 21cm signal has been removed. 
	--conclusions from this?
	--weird to me how the units of the streaming velocities are different. Change this?
	--unbolded addition to citation in caveat section

	--need to add the Hirano+18 science paper to caveats section

	Schauer+19 and Hirano+18 have been added to the introduction (unbolded -- fix this?).

	The sentence "Often in the literature, streaming velocities are only studied for a few haloes" has been removed.
